article title

### 2022-07-25 pilon_gilles_glossary.tex
Add sources of variation
Add range chart

>>>>

\newglossaryentry{range_chart}
    name={range chart},
    description={It is a chart that plots the range of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.},
    plural={range charts}
\newglossaryentry{sources_of_variation}
    name={sources of variation},
    description={These are the factors in a process that cause variation on the dependent variable. These factors may vary in a deliberate manner (fixed effects), random manner (random effects), or mixed effects (fixed and random factors)}
